Embedding Dimension of Polyhedral Losses

### 2020-01-31 colt-20/embed-dim.tex
Changed my mind on something

\begin{proof}[Proof of Theorem \ref{thm:opt-iff-qfp}]
	\jessie{Move to appendix?}
    By Theorem \ref{thm:vertex-halfspace-opt}, it suffices to show that $\T$ satisfying the halfspace and vertex conditions exist if and only if the program is feasible.

>>>>

\begin{proof}[Proof of Theorem \ref{thm:opt-iff-qfp}]
    By Theorem \ref{thm:vertex-halfspace-opt}, it suffices to show that $\T$ satisfying the halfspace and vertex conditions exist if and only if the program is feasible.
